Generalized Plackett-Luce Likelihoods

### 2022-10-10 inst/j_sports_econ_F1points.tex
issue #181 refers

\begin{titlepage}
  \begin{center}{\Large
      An objective assessment of point scoring systems in Formula 1 motor racing}\\
    Robin K. S. Hankin\\
{\tt hankin.robin@gmail.com}\\
Auckland University of Technology
\end{center}

@@

\section{\centering Introduction}\label{introduction}
Formula 1 motor racing is an important and prestigious motor sport
\citep{codling2017,jenkins2010}.  Season ranking is based on a points
allocation system wherein competitors are awarded points based on race
finishing order; points accumulate additively.  The overall
competition winner is the competitor who accumulates the most points
after the final race.

@@

\section{\centering Formula 1 dataset}\label{formula-1-dataset}

@@

\section{\centering Conclusions}

@@

%% BibTeX support
\bibliographystyle{apalike2}
\bibliography{formula1}

>>>>

\begin{titlepage}
  \begin{center}{\Large
      An objective assessment of point scoring systems in Formula 1 motor racing}\\
    name redacted\\
{\tt email redacted }\\
affiliation redacted
\end{center}

@@

\section{Introduction}\label{introduction}
Formula 1 motor racing is an important and prestigious motor sport
\citep{codling2017,jenkins2010}.  Season ranking is based on a points
allocation system wherein competitors are awarded points based on race
finishing order; points accumulate additively.  The overall
competition winner is the competitor who accumulates the most points
after the final race.

@@

\section{Formula 1 dataset}\label{formula-1-dataset}

@@

\section{Conclusions}

@@

%% BibTeX support
\bibliographystyle{apalike2}
\begin{thebibliography}{}

\bibitem[Bakhrankova, 2011]{bakhrankova2011}
Bakhrankova, K. (2011).
\newblock Points scoring systems in {F}ormula 1: A game theoretic perspective.
\newblock In D. Klatte (Ed.), {\em Operations Research Proceedings}  (pp.\
  211--216).: Springer-Verlag.

\bibitem[Bradley, 1952]{bradley1952}
Bradley, R.~A. (1952).
\newblock Incomplete block rank analysis: On the appropriateness of the model
  for a method of paired comparisons.
\newblock {\em Biometrics}, 10(3), 375--390.

\bibitem[Codling, 2017]{codling2017}
Codling, S. (2017).
\newblock {\em Speed read {F1}}.
\newblock Motorbooks.
\newblock ISBN 978-0-7603-5562-6.

\bibitem[Emerson, 2007]{emerson2007}
Emerson, P. (2007).
\newblock {\em Designing an All-Inclusive Democracy---Consensual Voting
  Procedures for use in Parliaments, Councils and Committees}.
\newblock Springer-Verlag.
\newblock {I}{S}{B}{N} 978-3-540-33163-6.

\bibitem[Gay-Rees, 2019]{gayrees2019}
Gay-Rees, J. (2019).
\newblock {F}ormula 1: drive to survive.
\newblock Netflix documentary.

\bibitem[Hankin, 2010]{hankin2010}
Hankin, R. K.~S. (2010).
\newblock A generalization of the {D}irichlet distribution.
\newblock {\em Journal of Statistical Software}, 33(11), 1--18.

\bibitem[Hankin, 2017]{hankin2017}
Hankin, R. K.~S. (2017).
\newblock Partial rank data with the {hyper2} package: likelihood functions for
  generalized {B}radley-{T}erry models.
\newblock {\em The R Journal}, 9(2), 429--439.

\bibitem[Jenkins, 2010]{jenkins2010}
Jenkins, M. (2010).
\newblock Technological discontinuities and competitive advantage: a historical
  perspective on {F}ormula 1 motor racing 1950-2006.
\newblock {\em Journal of Management Studies}, 47(5), 884--910.

\bibitem[Luce, 1959]{luce1959}
Luce, R. (1959).
\newblock {\em Individual choice behaviour: A theoretical analysis}.
\newblock New York: Wiley.

\bibitem[Mastromarco \& Runkel, 2009]{mastromarco2009}
Mastromarco, C. \& Runkel, M. (2009).
\newblock Rule changes and competitive balance in {F}ormula {O}ne motor racing.
\newblock {\em Applied Economics}, 41(23), 3003--3014.

\bibitem[Mollica \& Tardella, 2014]{mollica2014}
Mollica, C. \& Tardella, L. (2014).
\newblock Epitope profiling via mixture modeling of ranked data.
\newblock {\em Statistics in Medicine}, 33, 3738--3758.

\bibitem[Plackett, 1975]{plackett1975}
Plackett, R.~L. (1975).
\newblock The analysis of permutations.
\newblock {\em Applied Statistics}, 24, 193--202.

\bibitem[Wood, 2020]{wood2020}
Wood, E. (2020).
\newblock {F}ormula {S}cout (published online).

\bibitem[Zipf, 1949]{zipf1949}
Zipf, G. (1949).
\newblock {\em Human Behavior and the Principle of Least Effort}.
\newblock Addison-Wesley.

\end{thebibliography}
